Automatic prostate cancer detection through \acs*{dce}-\acs*{mri} images: all you need is a good normalization

### 2016-08-10 02_methods/methods.tex
advance tofts

\begin{description}
  \item[Conversion of \ac{mri} signal intensity to concentration]

  \item[Estimation of patient-based \ac{aif} signal \textit{vs.} population-based \ac{aif} signal]
\end{description}

>>>>

\noindent where $\Conv$ is the convolution operator; $C_t(t)$ and $C_p(t)$ is the concentration of contrast agent in the tissue and in the plasma, respectively; $K_{trans}$, $k_{ep}$, and $v_p$ are the volume transfer constant, the diffusion rate constant, and the plasma volume fraction, respectively.

Therefore, Tofts model requires to:
(i) estimate an \ac{aif} signal to later compute $C_p(t)$, and
(ii) convert the \ac{mri} signal intensity into a concentration.

\begin{description}
  \item[Estimation of \ac{aif} signal] Two different strategies can be used to get an \ac{aif} signal:
    (i) compute a population-based \ac{aif} signal or
    (ii) estimate a patient-based \ac{aif} signal from the \ac{dce}-\ac{mri} data.

    The former approach
  \item[Conversion of \ac{mri} signal intensity to concentration]
\end{description}
